---
title: "Social Network Analysis <br/> Home Assignment 2"
author: 'Chagaev Vladislav'
date: "due date - 29.05.2016 23:59"
output:
  pdf_document:
    latex_engine: xelatex
    toc: yes
  html_document:
    toc: yes
---
# Graph models. Centrality metrics
Please send your reports to network.hse.2016@gmail.com with the subject of of the following structure:<br/>
*[MAGOLEGO SNA 2016] {LastName} {First Name} HA{Number}*

Late submission policy: -1 point per day

Use this file as a template for your report.\
Support your computations with figures and comments. Send ONLY .Rmd versions of your report with datasets for your social network. Anonymize your data if necessary.

```{r, echo=FALSE}
library(igraph)
library(rgexf)
library(ggplot2)
library(R.matlab)
```


## Task 1. Your social network

For the first task, you have to load your [vk.com](http://vk.com) network. Please follow the instructions posted on the course wiki or user [VK Application](vk.com/app3861133). For [FB](http://facebook.com) users try to use [NetVizz](http://thepoliticsofsystems.net/2010/03/netvizz-facebook-to-gephi/). If you did it correctly, you should have a GraphML file with your own network. Read it to R:

```{r}
src = read.gexf("vk-friends-9475706.gexf")
friends_graph <- gexf.to.igraph(src)

```

### 1. Degree distribution

First, plot degree distribution of your network in log-log scales:

```{r}
degree_dist <- degree.distribution(friends_graph, cumulative = TRUE)
plot(degree_dist, log="xy", main = "Cumulative degree distribution of my network", xlab = "friend degree (log)", ylab = "frequency (log)")

```

Is there any correspondence between actual degree distribution of your network and the Power Law distribution? If not, explain why.

Yes, it is.

Now, let's see how it would look if it was random. Produce Erdos-Renyi graph matching your real network (same number of nodes and same average degree). Compare it with your degree distribution.

```{r}
mean_degree <- mean(degree(friends_graph))
c <- vcount(friends_graph)
rnd <- erdos.renyi.game(c, mean_degree/c/2, type = "gnp", directed = TRUE)
rnd_dist <- degree.distribution(rnd, cumulative = TRUE)
plot(rnd_dist, log="xy", main = "Cumulative degree distribution of random network", xlab = "friend degree (log)", ylab = "frequency (log)")
```

My network distribution has a lot of vertices with degree more than 50 and maximum degree is around 200. Random network has more nodes with relatively small degree (~less than 30)

### 2. Compute centrality metrics

Compute for your network: 

* degree centrality

* closeness centrality

* betweenness centrality

* eigenvector centrality

* Bonacich power centrality

* Alpha centrality


```{r}
centralization.degree(friends_graph)$centralization

centralization.closeness(friends_graph, mode="all")$centralization

centralization.betweenness (friends_graph, directed = TRUE, nobigint = TRUE)$centralization

centralization.evcent (friends_graph, directed = TRUE, scale = FALSE, options = igraph.arpack.default)$centralization



```

Output six plots corresponding to six centrality metrics you've computed: 

* Use first names of your friends as node labels on the graph (you may hide this information if you wish -- change it by integer ID)
* Keep the same layout of the network
* Make node sizes and colours proportional to the respective centrality metrics

Hint: If you get stuck, lab 4 script might be helpful.

```{r fig.width = 10, fig.height = 10}
deg<-degree(friends_graph)
lay <- layout.fruchterman.reingold(friends_graph)
fine = 500
palette2 <- colorRampPalette(c('blue','red'))
degCol <- palette2(fine)[as.numeric(cut(deg,breaks = fine))]
vert_size <- ifelse(deg>50, 1/50*deg, 1)
par(mfrow=c(1,1))
plot(friends_graph, layout=lay, vertex.color=degCol, vertex.size=vert_size, vertex.label=NA, edge.width = 0.5, edge.arrow.size = 0.5, main="Degree centrality")

```

```{r fig.width = 10, fig.height = 10}
clos=closeness(friends_graph)
closCol = palette2(fine)[as.numeric(cut(clos,breaks = fine))]

plot(friends_graph,layout = lay, vertex.label=NA, vertex.color=closCol, vertex.size=clos*15000, edge.width = 0.5, edge.arrow.size = 0.5, main="Closeness centrality")
```

```{r fig.width = 10, fig.height = 10}
betw <- betweenness(friends_graph)
betwCol = palette2(fine)[as.numeric(cut(betw,breaks = fine))]
vert_size <- ifelse(betw>4000, 1/4000*betw, 1)
plot(friends_graph,layout = lay, vertex.color=betwCol, vertex.size=vert_size, vertex.label=NA, edge.width = 0.5, edge.arrow.size = 0.5, main="Betwenness centrality")
```

```{r fig.width = 10, fig.height = 10}
ev <- evcent(friends_graph)$vector
evCol = palette2(fine)[as.numeric(cut(ev,breaks = fine))]
vert_size <- ifelse(ev>0.2, 5*ev, 0.8)
plot(friends_graph,layout = lay, vertex.size=vert_size, vertex.color=evCol, vertex.label=NA, edge.width = 0.5, edge.arrow.size = 0.5, main="Eigenvector centrality")

```

Now, output top ten nodes in each ranking. Again, print only first names in your table to keep privacy:

```{r}
## Put your code here
sort(deg, decreasing = TRUE)[1:10]
sort(clos, decreasing = TRUE)[1:10]
sort(betw, decreasing = TRUE)[1:10]
sort(ev, decreasing = TRUE)[1:10]
```

In general, the result was expected, because I lived in several cities so there are some well-known people which I and my friends know. Also I have a lot of common friends with my wife because we were classmates. Closeness is almost the same for a lot of my friends. I did not manage with Bonacich and alpha.


## Task 2. Flickr network

In the second task, you will work with a large directed graph. 

Please download [flickr.mat](http://www.hse.ru/data/2015/05/01/1098247366/flickr.mat) 

*Data contains sparse matrix A and list of user names. This is a denser part of the Flickr photo sharing site friendship graph from 2006. Edge direction corresponds to friendship requests (following). Some of the links are reciprocal, others not*

It's a Matlab file. How to deal with it in R? There is a package `R.matlab`. Please install it and call `library(R.matlab)`

Now use `readMat` function to read the file and extract adjacency matrix and a list of user names:

```{r}
flickr <- readMat("flickr.mat")
fmatrix <- as.matrix(flickr[1]$A)
fnames=flickr[2]$names
```

Look at user names. You might want to remove spaces from the names. Use a function `gsub` to remove them:

```{r}
fnames=gsub(" ", "", fnames)
```

Now create a graph, output the number of vertices and edges:

```{r}
flicker_graph <- graph.adjacency(fmatrix, mode = "directed", weighted = NULL)
vcount(flicker_graph)
ecount(flicker_graph)

```

Compute in- and out- degree centralities, PageRank, Hubs and Authorities for this network:

```{r}
cdi <-centralization.degree(flicker_graph, mode = "in")$centralization

cdo <-centralization.degree(flicker_graph, mode = "out")$centralization

pr <- page.rank(flicker_graph)$vector

h <- hub.score(flicker_graph)$vector

auth <- authority.score(flicker_graph)$vector


```

Print top ten names in each ranking:

```{r}
deg_in<-degree(flicker_graph, mode = "in")
top_in <- sort(deg_in, decreasing = TRUE)[1:10]
fnames[which(deg_in %in% top_in)]

deg_out=degree(flicker_graph, mode = "out")
top_out <- sort(deg_out, decreasing = TRUE)[1:10]
fnames[which(deg_out %in% top_out)]

top_pr <- sort(pr, decreasing = TRUE)[1:10]
fnames[which(pr %in% top_pr)]

top_hub <- sort(h, decreasing = TRUE)[1:10]
fnames[which(h %in% top_hub)]

top_auth <- sort(auth, decreasing = TRUE)[1:10]
fnames[which(auth %in% top_auth)]

```

Produce the following plots:

* In-degree centralities versus out-degree centralities

* In-degree centralities versus authorities

* Out-degree centralities versus hubs

* Hubs versus authorities

* PageRank versus hubs

* PageRank versus authorities


```{r}
par(mfrow = c(2, 3)) 
plot(deg_in, deg_out, col="blue", xlab = "In degree", ylab = "Out degree")
plot(deg_in, auth, col="blue", xlab = "In degree", ylab = "Authority")
plot(deg_out, h, col="blue", xlab = "Out degree", ylab = "Hubs")
plot(h, auth, col="blue", xlab = "Hubs", ylab = "Authority")
plot(pr, h, col="blue", xlab = "Page Rank", ylab = "Hubs")
plot(pr, auth, col="blue", xlab = "Page Rank", ylab = "Authority")

```

1)You have to follow at least several people in order to be popular but it is not the rule. There are a lot of people who follow a lot of other people and they follow in response.
2)Than more out degree then more hub is.
3)Authority depends on in degree and vice versa.
4)A lot of hubs don't have authority.
5)In general, big hub has low page rank.
6)Page rank depends on Authority and vice versa.
