---
title: "Social Network Analysis <br/> Home Assignment 4"
author: 'Chagaev Vladislav'
date: "due date - 12.06.2016 23:59"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
---
# Network Epidemics

Please send your reports to network.hse.2016@gmail.com with the subject of of the following structure:<br/>
*[MAGOLEGO SNA 2016] {LastName} {First Name} HW{Number}*

Late submission policy: -1 point per day

Use this file as a template for your report.\
Support your computations with figures and comments. Send ONLY .Rmd versions of your report.

```{r, echo=FALSE}
library(igraph)
```
## SIR Model

You need to perform epidemic SIR model on different types of networks:
Try different parameters for network generation
```{r}
gl <- list()
gl$ba <- barabasi.game(n = 6301,m = 4 , directed=FALSE)
gl$er <- erdos.renyi.game(n = 6301, p.or.m = 0.001, type=c("gnp"))
gl$ws <- watts.strogatz.game(dim = 1, size = 6301, nei = 3, p = 0.01)
data <- read.table("Net.txt")
data <- t(as.matrix(data))
data <- data+1
gl$net <- graph(data)
ev_er <- evcent(gl$er)$value
ev_ba <- evcent(gl$ba)$value
ev_ws <- evcent(gl$ws)$value
ev_net <- evcent(gl$net)$value
no.clusters(gl$er)
no.clusters(gl$ba)
no.clusters(gl$ws)
no.clusters(gl$net)

``` 
There are disconnected graphs!
Moreover perform modeling on real peer-to-peer network [here](https://www.hse.ru/data/2016/04/21/1130159900/Net.txt)


Your goal is to perform a research on epidemics:
Use different values of parameters listed below
```{r}
beta <- 2
gamma <- 4
ntrials <- 100

# Running function sir for each element of list gl (list with graphs)
sim <- lapply(gl, sir, beta=beta, gamma=gamma, no.sim=ntrials)
```
at least 3 different versions, for example:

* betta (4 6 8)
* gamma (8 6 2)
* niter (100 500 1000)
    
*For some reason `beta` and `gamma` parameters should not be set below 0 and 1. Looks like they are somehow normilized during simulation.*

The code below can help you with plotting
```{r}
x.max <- max(sapply(sapply(sim, time_bins), max))
y.max <- 1.05 * max(sapply(sapply(sim, function(x) median(x)[["NI"]]), max, na.rm=TRUE))

plot(time_bins(sim$er),  median(sim$er)[["NI"]], type="l", lwd=2, col="blue", xlim=c(0, x.max), ylim=c(0, y.max), xlab="Time", ylab=expression(N[I](t)))
lines(time_bins(sim$ba), median(sim$ba)[["NI"]], lwd=2, col="gold")
lines(time_bins(sim$ws), median(sim$ws)[["NI"]],lwd=2, col="red")
lines(time_bins(sim$net), median(sim$net)[["NI"]],lwd=2, col="green")
legend("topright", c("ER", "BA", "WS", "NET"),col=c("blue", "gold", "red", "green"), lty=1)
```

You need to plot three values on the graphics: Number of infected, number of suseprible, number of recovered - all depends on time.
As a result of this task, you need to provide 12 plots (one for each network with 3 diferent parameters) with explanation.
```{r, fig.width = 10, fig.height = 10, warning=FALSE}
par(mfrow=c(3,1))
beta <- 2
gamma <- 4
ntrials <- 100

sim <- lapply(gl, sir, beta=beta, gamma=gamma, no.sim=ntrials)
x.max <- max(sapply(sapply(sim, time_bins), max))
y.max <- 1.05 * max(sapply(sapply(sim, function(x) median(x)[["NI"]]), max, na.rm=TRUE))

plot(time_bins(sim$er), median(sim$er)[["NI"]], type="l", lwd=2, col="blue", xlim=c(0, x.max), ylim=c(0, y.max), xlab="Time", ylab=expression(N[I](t)))
lines(time_bins(sim$ba), median(sim$ba)[["NI"]], lwd=2, col="gold")
lines(time_bins(sim$ws), median(sim$ws)[["NI"]],lwd=2, col="red")
lines(time_bins(sim$net), median(sim$net)[["NI"]],lwd=2, col="green")
legend("topright", c("ER", "BA", "WS", "NET"),col=c("blue", "gold", "red", "green"), lty=1)

y.max = 1.05 * max(sapply(sapply(sim, function(x) median(x)[["NS"]]), max, na.rm=TRUE))
plot(time_bins(sim$er), median(sim$er)[["NS"]], type="l", lwd=2, col="blue", xlim=c(0, x.max), ylim=c(0, y.max), xlab="Time", ylab=expression(N[S](t)))
lines(time_bins(sim$ba), median(sim$ba)[["NS"]], lwd=2, col="gold")
lines(time_bins(sim$ws), median(sim$ws)[["NS"]],lwd=2, col="red")
lines(time_bins(sim$net), median(sim$net)[["NS"]],lwd=2, col="green")
legend("topright", c("ER", "BA", "WS", "NET"),col=c("blue", "gold", "red", "green"), lty=1)

y.max = 1.05 * max(sapply(sapply(sim, function(x) median(x)[["NR"]]), max, na.rm=TRUE))
max(sapply(sapply(sim, function(x) median(x)[["NR"]]), max, na.rm=TRUE))
plot(time_bins(sim$er), median(sim$er)[["NR"]], type="l", lwd=2, col="blue", xlim=c(0, x.max), ylim=c(0, y.max), xlab="Time", ylab=expression(N[R](t)))
lines(time_bins(sim$ba), median(sim$ba)[["NR"]], lwd=2, col="gold")
lines(time_bins(sim$ws), median(sim$ws)[["NR"]],lwd=2, col="red")
lines(time_bins(sim$net), median(sim$net)[["NR"]],lwd=2, col="green")
legend("topright", c("ER", "BA", "WS", "NET"),col=c("blue", "gold", "red", "green"), lty=1)
beta/gamma
1/ev_er
1/ev_ba
1/ev_ws
1/ev_net
```
There is not epidemic spread. Because of the high rate of regeneration. WS is not affected at all. NET and BA has similar EV and has similar form.

```{r, fig.width = 10, fig.height = 10, warning=FALSE}
par(mfrow=c(3,1))
beta <- 6
gamma <- 6
ntrials <- 500

sim <- lapply(gl, sir, beta=beta, gamma=gamma, no.sim=ntrials)
x.max <- max(sapply(sapply(sim, time_bins), max))
y.max <- 1.05 * max(sapply(sapply(sim, function(x) median(x)[["NI"]]), max, na.rm=TRUE))

plot(time_bins(sim$er), median(sim$er)[["NI"]], type="l", lwd=2, col="blue", xlim=c(0, x.max), ylim=c(0, y.max), xlab="Time", ylab=expression(N[I](t)))
lines(time_bins(sim$ba), median(sim$ba)[["NI"]], lwd=2, col="gold")
lines(time_bins(sim$ws), median(sim$ws)[["NI"]],lwd=2, col="red")
lines(time_bins(sim$net), median(sim$net)[["NI"]],lwd=2, col="green")
legend("topright", c("ER", "BA", "WS", "NET"),col=c("blue", "gold", "red", "green"), lty=1)

y.max = 1.05 * max(sapply(sapply(sim, function(x) median(x)[["NS"]]), max, na.rm=TRUE))
plot(time_bins(sim$er), median(sim$er)[["NS"]], type="l", lwd=2, col="blue", xlim=c(0, x.max), ylim=c(0, y.max), xlab="Time", ylab=expression(N[S](t)))
lines(time_bins(sim$ba), median(sim$ba)[["NS"]], lwd=2, col="gold")
lines(time_bins(sim$ws), median(sim$ws)[["NS"]],lwd=2, col="red")
lines(time_bins(sim$net), median(sim$net)[["NS"]],lwd=2, col="green")
legend("topright", c("ER", "BA", "WS", "NET"),col=c("blue", "gold", "red", "green"), lty=1)

y.max = 1.05 * max(sapply(sapply(sim, function(x) median(x)[["NR"]]), max, na.rm=TRUE))
max(sapply(sapply(sim, function(x) median(x)[["NR"]]), max, na.rm=TRUE))
plot(time_bins(sim$er), median(sim$er)[["NR"]], type="l", lwd=2, col="blue", xlim=c(0, x.max), ylim=c(0, y.max), xlab="Time", ylab=expression(N[R](t)))
lines(time_bins(sim$ba), median(sim$ba)[["NR"]], lwd=2, col="gold")
lines(time_bins(sim$ws), median(sim$ws)[["NR"]],lwd=2, col="red")
lines(time_bins(sim$net), median(sim$net)[["NR"]],lwd=2, col="green")
legend("topright", c("ER", "BA", "WS", "NET"),col=c("blue", "gold", "red", "green"), lty=1)
beta/gamma
1/ev_er
1/ev_ba
1/ev_ws
1/ev_net
```
Betta and alpha are equal. Total time depends on the graph structure. ER, BA and NET have leap but WS is sloping.
Threshold for SIR is not 1/ev!! There was not epidemic but it was really close. We can see how graphs with similar EV differ because of the structure.

```{r, fig.width = 10, fig.height = 10, warning=FALSE}
par(mfrow=c(3,1))
beta <- 8
gamma <- 2
ntrials <- 1000

sim <- lapply(gl, sir, beta=beta, gamma=gamma, no.sim=ntrials)
x.max <- max(sapply(sapply(sim, time_bins), max))
y.max <- 1.05 * max(sapply(sapply(sim, function(x) median(x)[["NI"]]), max, na.rm=TRUE))

plot(time_bins(sim$er), median(sim$er)[["NI"]], type="l", lwd=2, col="blue", xlim=c(0, x.max), ylim=c(0, y.max), xlab="Time", ylab=expression(N[I](t)))
lines(time_bins(sim$ba), median(sim$ba)[["NI"]], lwd=2, col="gold")
lines(time_bins(sim$ws), median(sim$ws)[["NI"]],lwd=2, col="red")
lines(time_bins(sim$net), median(sim$net)[["NI"]],lwd=2, col="green")
legend("topright", c("ER", "BA", "WS", "NET"),col=c("blue", "gold", "red", "green"), lty=1)

y.max = 1.05 * max(sapply(sapply(sim, function(x) median(x)[["NS"]]), max, na.rm=TRUE))
plot(time_bins(sim$er), median(sim$er)[["NS"]], type="l", lwd=2, col="blue", xlim=c(0, x.max), ylim=c(0, y.max), xlab="Time", ylab=expression(N[S](t)))
lines(time_bins(sim$ba), median(sim$ba)[["NS"]], lwd=2, col="gold")
lines(time_bins(sim$ws), median(sim$ws)[["NS"]],lwd=2, col="red")
lines(time_bins(sim$net), median(sim$net)[["NS"]],lwd=2, col="green")
legend("topright", c("ER", "BA", "WS", "NET"),col=c("blue", "gold", "red", "green"), lty=1)

y.max = 1.05 * max(sapply(sapply(sim, function(x) median(x)[["NR"]]), max, na.rm=TRUE))
max(sapply(sapply(sim, function(x) median(x)[["NR"]]), max, na.rm=TRUE))
plot(time_bins(sim$er), median(sim$er)[["NR"]], type="l", lwd=2, col="blue", xlim=c(0, x.max), ylim=c(0, y.max), xlab="Time", ylab=expression(N[R](t)))
lines(time_bins(sim$ba), median(sim$ba)[["NR"]], lwd=2, col="gold")
lines(time_bins(sim$ws), median(sim$ws)[["NR"]],lwd=2, col="red")
lines(time_bins(sim$net), median(sim$net)[["NR"]],lwd=2, col="green")
legend("topright", c("ER", "BA", "WS", "NET"),col=c("blue", "gold", "red", "green"), lty=1)
beta/gamma
1/ev_er
1/ev_ba
1/ev_ws
1/ev_net
```
There was not an epidemic for NET even with such high value of betta. I think the cause may be disconnected or "bridge" graph structure.
