---
title: "Social Network Analysis <br/> Home Assignment 3"
author: 'Chagev Vladislav'
date: "due date - 05.06.2016 23:59"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
---
# Network communities
Please send your reports to network.hse.2016@gmail.com with the subject of of the following structure:<br/>
*[MAGOLEGO SNA 2016] {LastName} {First Name} HW{Number}*

Late submission policy: -1 point per day

Use this file as a template for your report.\
Support your computations with figures and comments. Send ONLY .Rmd versions of your report.

```{r, echo=FALSE}
library(igraph)

```


## Yahoo Music Network

For this assignment, you have to load [the part of Yahoo Music Network](https://drive.google.com/file/d/0Bwd5a7NScgMtNElfOFdSbE1UYnM/view). Archive contains network in GML format and corresponding list of artists.

```{r}
g <- read.graph("music2K.gml", format = "gml")
artists <- scan("artists.txt", what="", sep="\n")
V(g)$label = artists
```

Edges in this network appear if enough number of users have given ratings to both music bands. Note, that edges are weighted with similarity of the ratings.


### 1. Preprocessing

This network needs to be preprocessed. Do the steps, described on seminar, to make it look properly. How many vertices and edges were deleted?

```{r}
before_ver <- vcount(g)
before_edg <- ecount(g)

g <- delete.vertices(g, degree(g) == 0)
simplify(g)

after_ver <- vcount(g)
after_edg <- ecount(g)

before_ver - after_ver
before_edg - after_edg

```

### 2. Clustering

Define clusters for this networks using one of the algorithms described on lectures and seminars:
```{r}
c <- multilevel.community(g)
```

Compute density of obtained clusters:
```{r}
dens <- 1:length(c)
inner_con <-  1:length(c)
for (i in 1:length(c)) {
  temp_g <- induced.subgraph(g, which(c$membership == i))
  inner_con[i] <- ecount(temp_g)
  dens[i] <- graph.density(temp_g)
}
dens
```

Compute the ratio of inner clusters connections to outer ones:
```{r}
sum(inner_con) / ecount(g)

```


### 3. Visualization & interpretation

Visulize five of the most dense clusters. Use names of artists as node labels on the graph.
```{r}
top_dens_clusters <- which(dens %in% sort(dens, decreasing = TRUE)[1:5])
top_vert <- which(c$membership %in% top_dens_clusters)
top_graph <- induced.subgraph(g, top_vert)

```

<b> (Extra task) </b>Try to interpret (using Wikipedia or other resources) obtained clusters.

*I used gephi tool to visualize graph. The image is attached. Artists in the segments have similar Genres. For example freestyle, jazz and others*